---
title: "Descriptive Epidemiology"
output: 
  word_document:
    fig_width: 10
    fig_height: 8
    reference_docx: PHE_template.docx
---


```{r message=FALSE, warning=FALSE, include=FALSE, results='hide'}

#----------------------------------------------------------------------------
# mandatory parameters

organism.name.for.title = "Cryptosporidium parvum"

end.reporting.date = "2017-01-24"

recent.historic.weeks = 10

historic.year = 2013

data.file.name = "Dummy_data.csv"


#----------------------------------------------------------------------------
# optional filter parameters

# e.g. sex = c("Female",  "Male", "Unknown")
sex = NULL

# e.g. age = 19
age.lower = NULL 

# e.g. age = 50 
age.upper = NULL 

# e.g. local.authority = c("Exeter", "Cornwall")
local.authority = NULL

# e.g.laboratory = c("DERRIFORD HOSP. (PLYMOUTH)", "OXFORD JOHN RADCLIFFE") 
laboratory = NULL 

# e.g. requesting.organisation = c("GENERAL PRACTITIONER", "HOSPITAL INPATIENT")
requesting.organisation = NULL 

# e.g. specimen.type = c("STOOL", "FAECES")
specimen.type = NULL 

# travel = c("Yes", "No", "Unknown")
travel = NULL 


#----------------------------------------------------------------------------
# optional figure aesthetic parameters

day.label.break = 2

week.label.break = 1

month.label.break = 0


recent.tile.plot.text = TRUE

historic.tile.plot.text = TRUE

#----------------------------------------------------------------------------

wd = "C:/Users/daniel.gardiner/Desktop/Temp"


setwd(paste0(wd, "/R"))
source("z01.master.source.R")
```






+ **Data source:** SGSS
+ **Date report produced**: `r format(Sys.Date(), "%d/%m/%Y")`
+ **Organism:** `r organism.name.for.title`
+ **End of reporting period:** `r format(end.reporting.date, "%d/%m/%Y")`
+ **Centre:** South West
+ **Sex:** `r bullet.sex`
+ **Age:** `r bullet.age`
+ **Local authority:** `r bullet.la`
+ **Laboratory:** `r bullet.lab`
+ **Requesting organisation:** `r bullet.request`
+ **Specimen type:** `r bullet.spectype`
+ **Travel status:** `r bullet.travel`


 
#####

# Recent cases

This section describes cases with specimen dates between  `r recent.date.range`.

## Figure 1: Epidemic curve of cases `r recent.date.range` by day

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4}
epicurve.all.recent
```


## Figure 3: Epidemic curve of cases `r recent.date.range` by week

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4.5}
epicurve.all.recent.week
```


#####


## Figure 5: Tile plot of cases `r recent.date.range` by week

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=5}
tile.plot.all.all.recent.week
```


#####

## Figure 5: Epidemic curve of cases `r recent.date.range` by sex by day

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=5}
epicurve.sex.recent
```


## Figure 7: Epidemic curve of cases `r recent.date.range` by sex by week

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4.5}
epicurve.sex.recent.week
```


#####


## Figure 5: Tile plot of cases `r recent.date.range` by sex by week

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=5}
tile.plot.all.sex.recent.week
```


#####


## Figure 9: Epidemic curve of cases `r recent.date.range` by age group by day

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4.5}
epicurve.age.grp.recent
```



## Figure 11: Epidemic curve of cases `r recent.date.range` by age group by week

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4.5}
epicurve.age.grp.recent.week
```


#####

## Figure 13: Tile plot of cases `r recent.date.range` by age group by week, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=9}
tile.plot.all.age.grp.recent.week
```



#####


## Figure 16: Age-sex distribution of cases, `r recent.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=7}
age.sex.pyrimid.recent
```

A total of `r age.sex.pyrimid.recent.missing` cases are missing  in the figure above due to either missing sex and age group information.



#####

## Figure 19: Tile plot of cases `r recent.date.range` by local authority by week, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=10}
tile.plot.all.local.authority.recent.week
```

#####

## Figure 20: Tile plot of cases `r recent.date.range` by local authority by week, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=10}
tile.plot.row.local.authority.recent.week
```


#####

## Figure 5: Tile plot of cases `r recent.date.range` by laboratory by week, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=10}
tile.plot.all.laboratory.recent.week
```

#####

## Figure 5: Tile plot of cases `r recent.date.range` by laboratory by week, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=10}
tile.plot.row.laboratory.recent.week
```


#####

## Figure 13: Tile plot of cases `r recent.date.range` by requesting organisation by week, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.all.request.recent.week
```


#####

## Figure 13: Tile plot of cases `r recent.date.range` by requesting organisation by week, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.row.request.recent.week
```



#####

## Figure 13: Tile plot of cases `r recent.date.range` by specimen type by week, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.all.spectype.recent.week
```

#####

## Figure 13: Tile plot of cases `r recent.date.range` by specimen type by week, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.row.spectype.recent.week
```



#####


## Figure 5: Epidemic curve of cases `r recent.date.range` by travel status by day

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4.5}
epicurve.travel.recent
```


## Figure 7: Epidemic curve of cases `r recent.date.range` by travel status by week

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 8, fig.height=4.5}
epicurve.travel.recent.week
```



#####

## Figure 13: Tile plot of cases `r recent.date.range` by travel status by week, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=6.5}
tile.plot.all.travel.recent.week
```


#####

# Historic cases

## Figure 17: Line graph of cases by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.all.trend.month
```


## Figure 17: Cumulative line graph of cases by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.cum.all.trend.month
```

#####

## Figure 13: Tile plot of cases `r entire.date.range` by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=5}
tile.plot.all.all.trend.month
```





#####

## Figure 17: Line graph of cases by sex by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.sex.trend.month
```


## Figure 17: Cumulative line graph of cases by sex by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.cum.sex.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by sex by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=6}
tile.plot.all.sex.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by sex by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=6}
tile.plot.row.sex.trend.month
```


#####

## Figure 17: Line graph of cases by age group by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.age.grp.trend.month
```


## Figure 17: Cumulative line graph of cases by age group by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.cum.age.grp.trend.month
```

#####

## Figure 13: Tile plot of cases `r entire.date.range` by age group by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=8}
tile.plot.all.age.grp.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by age group by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=8}
tile.plot.row.age.grp.trend.month
```



#####

## Figure 13: Tile plot of cases `r entire.date.range` by local authority by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.all.local.authority.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by local authority by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.row.local.authority.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by laboratory by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.all.laboratory.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by laboratory by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.row.laboratory.trend.month
```



#####

## Figure 13: Tile plot of cases `r entire.date.range` by requesting organisation by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.all.request.trend.month
```

#####

## Figure 13: Tile plot of cases `r entire.date.range` by requesting organisation by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.row.request.trend.month
```




#####

## Figure 13: Tile plot of cases `r entire.date.range` by specimen type by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.all.spectype.trend.month
```

#####

## Figure 13: Tile plot of cases `r entire.date.range` by specimen type by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10.5}
tile.plot.row.spectype.trend.month
```



#####

## Figure 17: Line graph of cases by travel status by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.travel.trend.month
```


## Figure 17: Cumulative line graph of cases by travel status by year-month, `r entire.date.range`

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=4.5}
line.graph.cum.travel.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by travel status by year-month, shading according to relative count across all tiles

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=6}
tile.plot.all.travel.trend.month
```


#####

## Figure 13: Tile plot of cases `r entire.date.range` by travel status by year-month, shading according to relative count across tiles within the same rows

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=6}
tile.plot.row.travel.trend.month
```



#####

# Recent vs Historic cases


## Figure 27: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.all.recent.vs.historic
```

#####


## Figure 29: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by week by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.all.recent.vs.historic.week
```

#####

## Figure 28: Cumulative line graph of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=6}
line.graph.cum.all.recent.vs.historic
```

#####

## Figure 28: Tile plot comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by sex by yearly period, shading according to relative count across all tiles 

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
tile.plot.all.all.recent.vs.historic.week
```


#####

## Figure 27: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by sex by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.sex.recent.vs.historic
```


#####

## Figure 30: Epicurve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by sex by week by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=11}
epicurve.sex.recent.vs.historic.week
```



#####


## Figure 29: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by age group by week by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.sex.recent.vs.historic.week
```


#####

## Figure 27: Cumulative line graph  of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by sex by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
line.graph.cum.sex.recent.vs.historic
```




#####

## Figure 28: Tile plot comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by sex by yearly period, shading according to relative count across all within the same group

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
tile.plot.all.sex.recent.vs.historic.week

```


#####


## Figure 27: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by age group by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.age.grp.recent.vs.historic
```


#####


## Figure 29: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by age group by week by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.age.grp.recent.vs.historic.week
```


#####

## Figure 28: Tile plot comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by age group by yearly period, shading according to relative count across all within the same group

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
tile.plot.all.age.grp.recent.vs.historic.week
```


#####

## Table 3: Table of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by local authority by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=8}
panderOptions('table.split.table', Inf)
pander(table.la.recent.vs.historic)
```


#####

## Figure 49: Bar graph of cases comparing recent cases to histroic average of cases within `r recent.vs.historic.date.range` between `r entire.date.range` by local authority

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
bar.graph.la.recent.vs.historic
```


Note: only local authorities where the number of recent cases is greater than the historic avgerage are presented in the table above




#####

## Table 4: Table of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by laboratory by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=8}
panderOptions('table.split.table', Inf)
pander(table.lab.recent.vs.historic)
```

#####

## Figure 50: Bar graph of cases comparing recent cases to histroic average of cases within `r recent.vs.historic.date.range` between `r entire.date.range` by laboratory

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
bar.graph.lab.recent.vs.historic
```

Note: only laboratories where the number of recent cases is greater than the historic avgerage are presented in the table above



#####

## Table 4: Table of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by requesting organisation by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=8}
panderOptions('table.split.table', Inf)
pander(table.request.recent.vs.historic)
```

#####

## Figure 50: Bar graph of cases comparing recent cases to histroic average of cases within `r recent.vs.historic.date.range` between `r entire.date.range` by requesting organisation

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
bar.graph.request.recent.vs.historic
```

Note: only requesting organisations where the number of recent cases is greater than the historic avgerage are presented in the table above



#####

## Table 4: Table of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by specimen type by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=8}
panderOptions('table.split.table', Inf)
pander(table.spectype.recent.vs.historic)
```

#####

## Figure 50: Bar graph of cases comparing recent cases to histroic average of cases within `r recent.vs.historic.date.range` between `r entire.date.range` by specimen type

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
bar.graph.spectype.recent.vs.historic
```

Note: only specimen types where the number of recent cases is greater than the historic avgerage are presented in the table above



## Figure 27: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by travel status by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.travel.recent.vs.historic
```

#####


## Figure 29: Epidemic curve of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by travel status by week by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
epicurve.travel.recent.vs.historic.week
```


#####

## Figure 28: Cumulative line graph of cases comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by travel status by yearly period

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
line.graph.cum.travel.recent.vs.historic
```


#####

## Figure 28: Tile plot comparing recent cases to histroic cases within `r recent.vs.historic.date.range` between `r entire.date.range` by travel status by yearly period, shading according to relative count across all within the same group

```{r message=FALSE, echo=FALSE, warning=FALSE, fig.width= 9, fig.height=10}
tile.plot.all.travel.recent.vs.historic.week
```


































































